comgen-outline

### 2017-08-29 paper/comgen-paper.Rmd
small edits to gen from obs; begin editing gen from lang

Generalizations are used to make predictions about properties instances that an agent has yet to experience [@HumeTHN]. 
From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
The properties can vary greatly (e.g. having fur, causing jitters, typing). 
Yet the prediction for a new entity can be described as a *predictive probability*: 
$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.
\ndg{say what we call $h$ throughout. prevalence?}

@@

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Observing some number of instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).

@@

Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
Observations that are generated by an intentional agent can similar lead to subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].

Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.

@@

@@

\begin{eqnarray}
\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
&\propto  &
\begin{cases}
1 & \text{if } h > \theta \\
0 & \text{otherwise}
\end{cases}
\end{eqnarray}

>>>>

Generalizations are used to make predictions about properties instances that an agent has yet to experience [@HumeTHN]. 
From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
The properties can vary greatly (e.g., having fur, causing jitters, typing). 
Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **prevalence**: 
$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
We denote prevalence as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency.
]

@@

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Observing some number of instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
As a concrete example, consider the feature \textsc{is friendly} ($f$) for the category \textsc{dog} ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
If an agent were to encounter some number of individual dogs and note how many of them were friendly ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).

@@

Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
This subtlety can be modeled using heirarchical models to provide structure to the prior distribution in a Bayesian model [@Kemp2008].
Observations that are generated by an intentional agent can lead to similarly subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].

Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to costly to observe (e.g., *starting at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.

@@

If generalization from observations can be described using probability, then it seems very natural to consider the semantic content of generalizations in language as relating to probability. 
One very simple semantic theory that has been used for describing quantified statements is a *threshold semantics*:

@@
